Analyzing the impact of social attributes on the success of commit integration

### 2017-02-17 Paper/MSRChallenge2017.tex
added the results

\begin{abstract}
\todo{Abstract goes here}
\end{abstract}

\begin{IEEEkeywords}
social attributes; Travis CI; Github; social networks; predicting integration success; social coding

\end{IEEEkeywords}

>>>>

\begin{abstract}
One important aspect of developing open source software is deciding which
commits to include in the main branch of a project.  
Recent research has started to explore how the open source community manages
this question and found that both technical and social factors are factors in 
the success of project contributions on GitHub.  
This investigation defined a successful project contribution as a project
contribution that gets
accepted to the project.  However, with the continuous integration, we can
explore this question a step further.  We can better estimate the success of a
contribution by investigating if the contribution passed the project's
test cases.  We performed an initial investigation into the technical and
social factors involved in a commit that successfully passes the integration
tests. Specifically, we investigated if social factors (such as being a
core member of the development team, having a large number of followers,
or contributing a large number of commits) improve predictions of build
success.  We have found that while social factors cause an noticeable increase
in predictive power (12\%), further investigation into these factors are
required.
\end{abstract}

\begin{IEEEkeywords}
Social Attributes; Travis CI; Github; Social Networks; Predicting Integration 
Success; Social Coding
\end{IEEEkeywords}
